Ore Polynomials in Sage

### 2013-06-18 paper/main.tex
version of gpl added to copyright notice, as suggested by Fredrik.
development version switched off.

THIS IS VERSION 0.1

 \bibliographystyle{plain}
 \bibliography{main}

>>>>

% \bibliographystyle{plain}
% \bibliography{main}

\begin{thebibliography}{10}

\bibitem{abramov03}
Sergei~A. Abramov, Ha~Q. Le, and Ziming Li.
\newblock {OreTools:} a computer algebra library for univariate ore polynomial
  rings.
\newblock Technical Report CS-2003-12, University of Waterloo, 2003.

\bibitem{abramov99}
Sergei~A. Abramov and Mark van Hoeij.
\newblock Integration of solutions of linear functional equations.
\newblock {\em Integral transforms and Special Functions}, 9:3--12, 1999.

\bibitem{bronstein96}
Manuel Bronstein and Marko Petkov{\v s}ek.
\newblock An introduction to pseudo-linear algebra.
\newblock {\em Theoretical Computer Science}, 157(1):3--33, 1996.

\bibitem{chyzak98a}
Fr{\'e}d{\'e}ric Chyzak.
\newblock {\em Fonctions holonomes en calcul formel}.
\newblock PhD thesis, INRIA Rocquencourt, 1998.

\bibitem{chyzak98}
Fr{\'e}d{\'e}ric Chyzak and Bruno Salvy.
\newblock Non-commutative elimination in {O}re algebras proves multivariate
  identities.
\newblock {\em Journal of Symbolic Computation}, 26:187--227, 1998.

\bibitem{hebisch11}
Waldemar Hebisch and Martin Rubey.
\newblock Extended {R}ate, more {GFUN}.
\newblock {\em Journal of Symbolic Computation}, 46(8):889--903, 2011.

\bibitem{jaroschek13b}
Maximilian Jaroschek.
\newblock Improved polynomial remainder sequences for {Ore} polynomials.
\newblock {\em Journal of Symbolic Computation}, 2013.
\newblock to appear.

\bibitem{jaroschek13a}
Maximilian Jaroschek, Manuel Kauers, Shaoshi Chen, and Michael~F. Singer.
\newblock Desingularization explains order-degree curves for {Ore} operators.
\newblock In Manuel Kauers, editor, {\em Proceedings of ISSAC'13}, 2013.
\newblock to appear.

\bibitem{kauers09a}
Manuel Kauers.
\newblock Guessing handbook.
\newblock Technical Report 09-07, RISC-Linz, 2009.

\bibitem{kauers13}
Manuel Kauers.
\newblock The holonomic toolkit.
\newblock In Johannes Bluemlein and Carsten Schneider, editors, {\em Computer
  Algebra in Quantum Field Theory: Integration, Summation and Special
  Functions}, Texts and Monographs in Symbolic Computation. Springer, 2013.

\bibitem{koutschan09}
Christoph Koutschan.
\newblock {\em Advanced Applications of the Holonomic Systems Approach}.
\newblock PhD thesis, RISC-Linz, Johannes Kepler Universit{\"a}t Linz, 2009.

\bibitem{koutschan10c}
Christoph Koutschan.
\newblock {HolonomicFunctions (User's Guide)}.
\newblock Technical Report 10-01, RISC Report Series, University of Linz,
  Austria, January 2010.

\bibitem{li96}
Ziming Li.
\newblock {\em A Subresultant Theory for Linear Differential, Linear
  Difference, and {O}re Polynomials, with Applications}.
\newblock PhD thesis, RISC-Linz, 1996.

\bibitem{mallinger96}
Christian Mallinger.
\newblock Algorithmic manipulations and transformations of univariate holonomic
  functions and sequences.
\newblock Master's thesis, J. Kepler University, Linz, August 1996.

\bibitem{ore33}
{\O}ystein Ore.
\newblock Theory of non-commutative polynomials.
\newblock {\em Annals of Mathematics}, 34:480--508, 1933.

\bibitem{salvy94}
Bruno Salvy and Paul Zimmermann.
\newblock {G}fun: a {M}aple package for the manipulation of generating and
  holonomic functions in one variable.
\newblock {\em ACM Transactions on Mathematical Software}, 20(2):163--177,
  1994.

\bibitem{sage}
W.\thinspace{}A. Stein et~al.
\newblock {\em {S}age {M}athematics {S}oftware (Version 5.9)}.
\newblock The Sage Development Team, 2013.
\newblock {\tt http://www.sagemath.org}.

\end{thebibliography}
